Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-11 CJM/letter to CJM.tex
Move comment to letter

\begin{enumerate}
\item[(1)] We are extremely grateful for this observation. We had made a mistake. Previously, we considered a category of triples $(\cs{L},\mu,\nu)$ with a compatibility condition on $\mu : a^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu : n^* \cs{L}\to (\EE)_{H}\boxtimes \cs{L}$. But that compatibility condition had the error built into it that was noticed in the review. In the process of fixing the error, we found that it was more natural to drop the compatibility condition entirely and replace $\mu$ as above with $\mu : n^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, where $n: G\der\times G\to G$ is the restriction of the group action from $G\times G$ to $G\der\times G$. Also, in an effort to improve clarity of presentation of Section 3, we moved the proofs from the last subsection back into the flow of the paper, made some notational changes, and added exposition.
Fortunately, this had the effect of simplifying the constructions and did not add to the length of the paper. 
\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review. Our main motivation for Sections 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups. (Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
\end{enumerate}

>>>>

\begin{enumerate}
\item[(1)] We are extremely grateful for this observation. We had made a mistake. Previously, we considered a category of triples $(\cs{L},\mu,\nu)$ with a compatibility condition on $\mu : a^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu : n^* \cs{L}\to (\EE)_{H}\boxtimes \cs{L}$. But that compatibility condition had the error built into it that was noticed in the review. In the process of fixing the error, we found that it was more natural to drop the compatibility condition entirely and replace $\mu$ as above with $\mu : n^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, where $n: G\der\times G\to G$ is the restriction of the group action from $G\times G$ to $G\der\times G$. Also, in an effort to improve clarity of presentation of Section 3, we moved the proofs from the last subsection back into the flow of the paper, made some notational changes, and added exposition.
Fortunately, this had the effect of simplifying the constructions and did not add to the length of the paper. 
\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review. Our main motivation for Sections 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups. (Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.)

Observe that $\CCS(G)$ is a subcategory of $\CS\ab(G)$, by Definition~3.2, and that Definition~3.1 makes it clear that there is a forgetful functor $\CS\ab(G) \to \CS(G)$, and also a forgetful functor $\CS(G)\to \Loc(G)$.
Consequently, while the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the sense of Theorem~3.12, it is also true that $\CS(G)$ and even $\Loc(G)$
geometrize characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
However, category $\CCS(G)$ has made this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{} : \CCSiso{G} \to G(k)^*$ as close to an isomorphism as possible.
\end{enumerate}
